---
always_allow_html: true
---

```{r warning=FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
source(here::here("tables", "_common.R"))
```

# Tables intro

This chapter shows a few simple examples of including tables and getting cross-referencing to work across formats (HTML, Word, PDF). See @sec-kableflexgt for more examples and comparisons of different table outputs.

In this chapter, I am going to use {flextable} for Word and HTML and {kabelExtra} for PDF. See @sec-kableflexgt for a comparison of {flextable}, {kableExtra} and {gt}. There is a current problem that Quarto is not processing the cross-references with {flextable} into PDF and Word. But this is a known problem and they are working on it. {flextable} is the only table package that I have found the tends to work as expected across platforms. The {officer} package uses it so it works well with Word and works well with LaTeX.

*Note, I am using some customized functions to be able have a uniform look for my tables. These are in `tables/_common.R`.


## Example table

This is an example a table. We can reference @tbl-example easily and it is auto-numbered. 

```{r}
#| label: tbl-example
#| tbl-cap: "This is a simple table."
dt <- mtcars[1:10, 1:6]
if(table.engine=="flextable") myflextable(dt)
if(table.engine=="kbl") mykbl(dt)
```

## Including table files

It is often good to have your files in separate files so that when you edit your tables, you only have to work on the table code.

````markdown
`r ''````{r child=here::here("tables", "Table_flex.Rmd")}
```
````

```{r child=here::here("tables", "Table_flex.Rmd")}
```


## Cross-references

In Quarto, [table links](https://quarto.org/docs/authoring/cross-references.html#tables) use the table label `@tbl-tablabel` where `tablabel` is the label you put on the table chunk. In the text it looks like this @tbl-tablabel. The chunk yaml looks like this

```
#| label: tbl-tablabel
#| tbl-cap: "my caption"
```

```{r}
#| label: tbl-tablabel
#| tbl-cap: "This is a table with a number."
tt <- ts(cumsum(1 + round(rnorm(100), 0)),
    start = c(1954, 7), frequency = 12)
Month <-  factor(cycle(tt), levels = 1:12, labels = month.abb)
dt <- as.data.frame(tapply(tt, list(year = floor(time(tt)), month = Month), c))
dt <- dt %>% tibble::rownames_to_column("Year")
if(table.engine=="flextable") myflextable(dt)
if(table.engine=="kbl") mykbl(dt)
```

## Dynamic table captions

You can create captions dynamically.

```{r}
#| echo: true
dt <- mtcars[1:10, 1:6]
tbl_cap <- paste("This is a dynamically created caption. The length of mtcars is", nrow(mtcars), "rows. Here we show", nrow(dt), "rows.")
```

Unfortunately you cannot dynamically create your chunk labels too.

```{r}
#| label: tbl-test3
#| tbl-cap: !expr tbl_cap
if(table.engine=="flextable") myflextable(dt)
if(table.engine=="kbl") mykbl(dt)
```

